\documentclass[9pt]{beamer}

\usepackage{booktabs}
\usepackage{geometry}
% \usepackage{enumitem}
\usepackage{textcomp}

\usetheme{Copenhagen}

\title{Knowledge Grounding in Retrieval-Augmented LMs \\ The update before the holidays}
\author{Martin Fixman (coming from Argentina)}
\institute{City St.\ Georges, University of London}
\date{December 20, 2024}

\begin{document}

\begin{frame}
	\titlepage{}
\end{frame}

\section{Quick Personal Update}
\begin{frame}{Quick Personal Update: what has Martin been working on?}
	\pause{}
	\emph{Rough} 2025 Timeline: \\[20pt]

	\begin{description}[labelwidth=75pt]
		\item[January 15] I return from Argentina.
		\item[January 15 -- May] Working in papers to present to workshops.
		\item[May -- October] Continuing enhancing and presenting papers.
		\item[October] Martin (ideally) starts PhD. End writing work. \\[10pt]
		\item[Afterwards] Presenting remaining papers.
	\end{description}
\end{frame}

\section{Deadlines and Conferences}
\begin{frame}{Deadlines}
	Current goal: put the paper in a workshop \emph{as soon as possible}.

	\begin{itemize}
		\item \textbf{ACL} Main Conference: February 15.
		\item \phantom{\textbf{ACL}} Workshop: May 18. \\[10pt]
		\item \textbf{ICML} Main Conference: January 23.
		\item \phantom{\textbf{ICML}} Workshop: ? \\[10pt]
		\item \textbf{ICJNN} Main Conference: January 15.
		\item \phantom{\textbf{ICJNN}} Workshop: ?
	\end{itemize}
\end{frame}

\begin{frame}{Current State of the Paper}
	\begin{enumerate}
		\item New references were added.
		\item Experimental methods were rewritten, althrough this could be done better.
		\pause{}
		\item Still a lot of work to do!
	\end{enumerate}
\end{frame}

\section{Areas to expand in the paper}
\begin{frame}{Areas to expand in the paper}
	\begin{itemize}
		\item \textbf{Last minute additions}
			\begin{itemize}
				\item Attention part.
				\item Contextual-or-parametric classifier.
			\end{itemize}
		\item \textbf{Future work}
			\begin{itemize}
				\item Using ATLAS and similar models.
				\item Better categorisation of the answers.
				\item Natural Questions dataset.
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Thank you!}
	\centering
	\Huge
	Have a good 2025!
\end{frame}

\end{document}
